Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
wordings.

In BDD, all behavior should be documented, together with some
\emph{evidence}\/s for that behavior.
for this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation, we also make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

@@

\item[user documentation]
    TBD: Explanation of functions.
\item[code documentation]
    TBD: Explanation of functions.

@@

We can categorize evidences into two types: for users and
and for developers.
evidences for users are those which are useful as user documentation.
By contrast, evidences for developers are
those which are not useful as user documentation.
A good example of evidences for developers
is a corner example registered in a bug tracking system.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidence as user documentation}
\label{sec:for-users}

evidences for users should be documented with Haddock markup syntax.
For this purpose, we propose the followings:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidence as code documentation (TBD: Is this still
appropriate here?}
\label{sec:for-developers}

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence}\/s for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation, we also make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

@@

\item[user documentation]
    Explanation of functions for users.
\item[code documentation]
    Explanation of functions for developers.

@@

We can categorize evidences into two types: for users and
and for developers.
Evidences for users are those which are useful as user documentation.
By contrast, evidences for developers are
those which are not useful as user documentation
but should be written as code documentation.
A good example of evidences for developers
is a corner example registered in a bug tracking system.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidences as user documentation}
\label{sec:for-users}

Evidences for users should be documented with Haddock markup syntax.
For this purpose, we propose the followings:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidences as code documentation (TBD: Is this still
appropriate here?}
\label{sec:for-developers}
